
%\documentclass[10pt, conference, compsocconf]{IEEEtran}


%\hyphenation{op-tical net-works semi-conduc-tor}


%\begin{document}
%
% paper title
%
% can use linebreaks \\ within to get better formatting as desired
%\title{Studying the Impact of Logging Practices on Code Quality of Systems Software}


% author names and affiliations
% use a multiple column layout for up to two different
% affiliations

%\author{\IEEEauthorblockN{Weiyi Shang, Meiyappan Nagappan, Ahmed E. Hassan, Emad Shihab}
%\IEEEauthorblockA{Software Analysis and Intelligence Lab (SAIL)\\ Queen's University\\
%Kingston, Ontario, Canada\\
%\{swy, mei, ahmed, emad\}@cs.queensu.ca}
%}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
%\maketitle




\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\input{setup}

\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{balance}
\usepackage{amssymb,amsmath}
\usepackage{wrapfig}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{times}
\usepackage{cite}
\usepackage{fancybox}
\usepackage{color}
\usepackage{array}
\usepackage{subfigure}
\usepackage{epstopdf}
\usepackage{booktabs}
\usepackage{caption,fixltx2e}
\usepackage[flushleft]{threeparttable}
%\usepackage{subfig}
%\usepackage{xspace}
\usepackage[hyphens]{url}
\usepackage[hidelinks]{hyperref}
\hypersetup{breaklinks=true}
\urlstyle{same}
\def\UrlBreaks{\do\/\do-} %to break the urls, all in one line
\newcommand{\ian}[1]{\textcolor{blue}{{\it [Ian: #1]}}}
\newcommand{\emad}[1]{\textcolor{green}{{\it [Emad: #1]}}}
\newcommand{\todo}[1]{\textcolor{red}{{\it [TODO: #1]}}}


\newcommand{\conclusionbox}[1]{%
	\vspace{2mm}
	\framebox[0.45\textwidth][c]{%
		\parbox[b]{0.42\textwidth}{%
			{\it #1}
		}
	}
	\vspace{2mm}
}

%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Empirical Study on the Discrepancy between Performance Testing Results from Virtual and Physical Environments}

%\subtitle{Do you have a subtitle?\\ If so, write it here}

\titlerunning{Discrepancy between Performance Testing Results between diff. environments}        % if too long for running head

\author{Muhammad Moiz Arif \and Weiyi Shang \and Emad Shihab
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{Muhammad Moiz Arif , Weiyi Shang, Emad Shihab\at
              Department of Computer Science and Software Engineering\\
		Concordia University\\
			Montreal, Quebec, Canada\\
              \email{\{mo\_ari, shang, eshihab\}@cse.concordia.ca}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
%          \and
%           Meiyappan Nagappan \at
%		              Software Analysis and Intelligence Lab (SAIL)\\
%					Queen's University\\
%					Kingston, Ontario, Canada\\
%		              Tel.: +1 613-533-6802\\
%		              \email{mei@cs.queensu.ca}
%					   \and
%			 Ahmed E. Hassan\at
%	          	Software Analysis and Intelligence Lab (SAIL)\\
%					Queen's University\\
%					Kingston, Ontario, Canada\\
%		             Tel.: +1 613-533-6802\\
%		            \email{ahmed@cs.queensu.ca}
%		   \and
%	          Emad Shihab\at
%				Software Analysis and Intelligence Lab (SAIL)\\
%					Queen's University\\
%					Kingston, Ontario, Canada\\
%			Tel.: +1 613-533-6802\\
%		\email{emad@cs.queensu.ca}
}

\date{Received: date / Accepted: date}


\maketitle

\makeatletter
\def\ps@headings{%
\def\@oddfoot{\scriptsize \hfill \thepage }%
\def\@evenfoot{\scriptsize \thepage \hfill}}
\makeatother
\pagestyle{headings}

\begin{abstract}
Large software systems often undergo performance tests to ensure their capability to handle expected loads. These performance tests often consume large amounts of computing resources and time since heavy loads need to be generated. Making it worse, the ever evolving field requires frequent updates to the performance testing environment. In practice, virtual machines (VMs) are widely exploited to provide flexible and less costly environments for performance tests. However, the use of VMs may introduce extra overhead (e.g., a higher than expected memory utilization) to the testing environment and lead to unrealistic performance testing results. Yet, little or no research has studied the overhead and impact on test results of using VMs in performance testing activities. 

To evaluate the discrepancy between the performance testing results from virtual and physical environments, we perform a case study on two open source systems - namely Dell DVD Store and CloudStore. We conduct the same performance tests in both virtual and physical environments and compare the performance testing results based on the three aspects that are typically examined for performance testing results: 1) individual performance metrics (e.g. CPU Time vs CPU Time), 2) the relationship among performance metrics (one-to-many relationship) and 3) performance models that are built to predict future performance. Our results show that 1) individual performance metrics from virtual and physical environments do not follow the same distribution hence practitioners can not simply use a scaling factor to compare the performance between environments,  2) correlations among performance metrics in virtual environments are different from the correlations in physical environments which implies that the aforementioned change in correlations may not be just because of a performance discrepancy and 3) statistical models built based on the performance counters from virtual environments are different from the models built from physical environments suggesting that practitioners need to normalize the performance metrics. We also investigate ways to transform results from virtual and physical environments ang performance metrics based on deviance may reduced the discrepancy between performance metrics. Overall, we recommend that practitioners should not simply assume that performance testing results done on virtual environments will be the same in physical environments.

%be aware of such discrepancy and may leverage normalization techniques when analyzing performance testing results from the virtual environments.




%	activities, including performance modeling and performance regression detection. The two activities are conducted in both environments that consists of physical machines or VMs. We observed that the comparison between the virtual and physical environments is not straight forward. We also observed that the performance of our subject systems between two environments is not identical.

%	\textcolor{red}{(insert implications)}

%	\textit{Keywords--Performance engineering; Performance testing; Performance modeling; Performance analysis}	
\end{abstract}

%\begin{IEEEkeywords}
%Software maintenance, Mining software repositories, Software logs, Software quality
%\end{IEEEkeywords}

%\IEEEpeerreviewmaketitle
%\vspace{-0.2cm}


\section{Introduction}
%\vspace{-0.1cm}
\label{sec:intro}
\input{intro}

\section{Background and Related Work}
%\vspace{-0.1cm}
\label{sec:related}
\input{related}

\section{Case Study Setup}
%\vspace{-0.1cm}
\label{sec:case}
\input{case}


\section{Case Study Results}
%\vspace{-0.1cm}

\label{sec:results}
\input{results}

\section{Discussion}
\label{sec:discussion}
\input{discussion}
	
\section{Threats to Validity}
%\vspace{-0.1cm}
\label{sec:threats}
\input{threats}


\section{Conclusion}
%\vspace{-0.1cm}

\label{sec:conclusion}
\input{conclusion}

%\section*{Acknowledgment}

%The author thanks Emad Shihab and Thanh H$.$D$.$ Nguyen for their suggestions on the early version of this work. The author appreciates the generosity of the Performance Engineering team at Research In Motion (RIM). Working with the team as an embedded researcher, the author has gained an appreciation of the current practice of mining large-scale software logs.

\bibliographystyle{spmpsci}
\bibliography{references}
%\balance

\end{document}


