\documentclass[12pt]{report}


%\usepackage{color}
\usepackage{url}
\usepackage{xspace}
\usepackage{cuthesis}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{csquotes}
%\usepackage{pdflscape}
\usepackage{subfigure}
%\usepackage[framemethod=TikZ]{mdframed}
\usepackage{amssymb,amsmath}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{fancybox}
\usepackage[flushleft]{threeparttable}
\usepackage{framed}
\usepackage{breakcites}
\usepackage{microtype}
\usepackage{pdflscape}


\linespread{1.6}

\author{Muhammad Moiz Arif}
\title {An Empirical Study on the Discrepancy between Performance Testing Results from Virtual and Physical Environments}
\degree{Master of Applied Science in Software Engineering}
\dept  {Computer Science and Software Engineering}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% define commands for frequently used words or phrases
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \newcommand{\SATD}{self-admitted technical debt\xspace}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% define commands for your RQs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\chapterIIIrqi}{\textbf{RQ:}}
\newcommand{\chapterIVrqi}{\textbf{RQ1. \\}}
\newcommand{\chapterIVrqii}{\textbf{RQ2. \\}}
\newcommand{\chapterIVrqiii}{\textbf{RQ3. \\}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% define command to create a conclusion box to answer your RQs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\conclusionbox}[1]{%
    \vspace{6mm}
    \framebox[0.95\textwidth][c]{%
        \parbox[b]{0.92\textwidth}{%
            {\it #1}
        }
    }
    \vspace{6mm}
}


\begin{document}

\begin{abstract}
Large software systems often undergo performance tests to ensure their capability to handle expected loads. These performance tests often consume large amounts of computing resources and time since heavy loads need to be generated. Making it worse, the ever evolving field requires frequent updates to the performance testing environment. In practice, virtual machines (VMs) are widely exploited to provide flexible and less costly environments for performance tests. However, the use of VMs may introduce confounding overhead (e.g., a higher than expected memory utilization with unstable I/O traffic) to the testing environment and lead to unrealistic performance testing results. Yet, little research has studied the impact on test results of using VMs in performance testing activities. 

To evaluate the discrepancy between the performance testing results from virtual and physical environments, we perform a case study on two open source systems -- namely Dell DVD Store (DS2) and CloudStore. We conduct the same performance tests in both virtual and physical environments and compare the performance testing results based on the three aspects that are typically examined for performance testing results: 1) single performance metric (e.g. CPU Time from virtual environment vs. CPU Time from physical environment), 2) the relationship among performance metrics (e.g. correlation between CPU and I/O) and 3) performance models that are built to predict system performance. Our results show that 1) A single metric from virtual and physical environments do not follow the same distribution, hence practitioners cannot simply use a scaling factor to compare the performance between environments,  2) correlations among performance metrics in virtual environments are different from those in physical environments 3) statistical models built based on the performance metrics from virtual environments are different from the models built from physical environments suggesting that practitioners cannot use the performance testing results across virtual and physical environments. In order to assist the practitioners leverage performance testing results in both environments, we investigate ways to reduce the discrepancy. We find that such discrepancy can be reduced by normalizing performance metrics based on deviance. Overall, we suggest that practitioners should not use the performance testing results from virtual environment with the simple assumption of straightforward performance overhead. Instead, practitioners should consider leveraging normalization techniques to reduce the discrepancy before examining performance testing results from virtual and physical environments.


\end{abstract}

\begin{acknowledgments}

I would like to show my gratitude towards the people whose support and encouragement proved to be colossal throughout this journey. However, first, I thank Allah, for it is He who provided me with wisdom, health, capabilities, and desire to achieve my goals.
\\

My sincerest and deepest gratitude goes to my academic supervisors, Dr. Emad Shihab and Dr. Weiyi Shang. From the time of of accepting me as a student to the never giving up attitude till the end, I thank you. All my work, results, and the learning experiences would have been meaningless if it was not for your guidance, mentorship and undying support. I consider myself very lucky to have had the opportunity to learn from you.
\\

I would like to acknowledge my thesis committee, Dr. Juergen Rilling and \textbf{insert name} for taking the time out to read my thesis and providing valuable and constructive feedback. I also thank the Department of Engineering and Computer Science at Concordia University, for making my graduate experience immaculate.
\\

I am grateful to Thanh Nguyen with whom I worked under at Blackberry. His work remains the core of my thesis. I am indebted for the opportunity, exposures and practical suggestions provided. 
\\

I owe a debt of gratitude to all my fellow colleagues, 
Rabe Abdalkareem, Mehran Hassani, Davood Mazinanian, Maaz Hafeez Ur Rehman, Shahriar Rostami, Maxime Lamothe, Guilherme Pádua, Jinfu Chen, Kundi Yao, Suhaib Mujahid and Giancarlo Sierra. It was a pleasure to share the same labs as you guys. I wish you all immense success in your journeys. 
\\

It is a pleasure to thank my friends who inspired and supported me tirelessly through thick and thin. A special thanks to Everton da Silva Maldonado, Ahmed Sukhera, Syed Ali Sattam \& Ahmad Al-Sheikh Hassan. You guys always fueled me with utmost motivation. I am proud to call you my closest friends. 
\\





\end{acknowledgments}

\begin{dedication}
	\begin{flushright}
		\textit{To my parents.}
	\end{flushright}

	
\end{dedication}

\begin{publications}

The following publications are related to this thesis:

\begin{enumerate}

\item {\textbf{Muhammad Moiz Arif}, Weiyi Shang, \& Emad Shihab. Empirical Study on the Discrepancy between Performance Testing Results from Virtual and Physical Environments. In \textit{Empirical Software Engineering Journal (EMSE)}, 2017. \textbf{[Major Revision]}} 

%\item \textbf{Moiz}, 
\end{enumerate}

\end{publications}

\chapter{Introduction}
\label{introduction}
\input{introduction.tex}

\chapter{Background and Literature Review}
\label{background_and_literature_review}
\input{background_and_literature_review.tex}

\chapter{Testing For The Ubiety Of Discrepancy}
\label{chapter3}
\input{chapter3.tex}

\chapter{Studying The Impact Of Modifying The Virtual Environment}
\label{chapter4}
\input{chapter4.tex}

\chapter{Summary, Contributions and Future Work}
\label{conclusion}
\input{conclusion.tex}

\chapter{Appendix}
\label{appendix}
\input{appendix.tex}

%\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{bibliography.bib}  
\bibliographystyle{alpha}
\end{document}