In our research questions we concluded that comparing the physical and virtual environment and using the performance metrics may not be as straight forward. One of the reasons that this might stand true is because of the instability of the virtual environment itself. We now try to explore the if there are any discrepancy present in the nature of our virtual environment.

\subsection{Repeatability}
In order to check whether the performance test done in virtual environment are repeatable or whether the environment itself is instable, we carried out two more tests for each of our subject system. We trained our models on the new repeated tests and tested it on the baseline test used in our research question. The experiment was a replica of our previous experiments.
\\
\\
\framebox{\begin{varwidth}{\textwidth}\textit{Yes, the performance tests carried out in the virtual environment are repeatable.}\end{varwidth}}


%\fbox{\textit{Yes, the performance tests carried out in the virtual environment are repeatable.}}

%Yes, the performance tests carried out in the virtual environment are repeatable.

\subsection{Resource Allocation}
Next, we altered the resources allocated to the guest OS. This helped us deduce whether resource allocation makes a difference in a model driven approach. We increased our resources from 2 cores and 3GB memory to 3 cores and 5GB memory. Similar to our previous approaches, we trained our model on the new set of performance metrics and tested it on the baseline test.
\\
\\
\framebox{\begin{varwidth}{\textwidth}\textit{Yes, a change in resource effects the performance of the subject system in the virtual environment}\end{varwidth}}

%\fbox{\textit{Yes, a change in resource effects the performance of the subject system in the virtual environment.}}

\subsection{Type of Virtual Environment}

We also investigated if the our subject systems behave similarly in different virtual environments. For this, we set up another type of virtual environment with the same specifications to provide an identical environment. 

\fbox{\textit{}}