This sections chalks out out the threats to our validity.
\subsection{External validity}
\textcolor{red}{discuss}
We chose two subject system for our study and VirtualBox as our virutal environment. All of the former mentioned entities have a credible history when it comes to the research are of performance engineering. \cite{5306331} \cite{Nguyen:2012:ADP:2188286.2188344}. Also, we made sure that our virtual environment is set up exactly the same as our physical environment by keeping a constant checks aided by scripts. Having said that, this study can be boosted by additional subject systems being tested on more than one type of virtual environment. 

\subsection{Internal Validity}

All of our models are dependent on the performance metrics' accuracy. Which means if the load on the server is beyond the capacity of the system to handle and builds up a queue, there is a possibility of noise sneaking in the recording process of the performance metrics. 
The scaling approach we have adopted assumes that the for a particular metric, there exists alpha and beta values. However, if the metric value is constant it not possible to have an alpha and beta value associated with it in the model. Hence looking for an alternate scaling process is necessary for such a performance metric.
We build performance regression models to compare the metrics from both of our environments. This models are accurate if there exists a high number of records for the performance counters. Additionally, we also assume that none of our dependent variable is correlated to the independent variable or vice-versa. 
